---
title: "Forecasting temperature at your vacation destination"
author: "M. Salmon"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

For Christmas I'll travel to Marseille. What temperatures should I expect there? I could of course open a weather app, but in this vignette I want to give an example using the `riem` and  `forecast` packages. 

# Find airport for Marseille

The name of the network for France is "FR__ASOS". I already know there's only one airport near the city.

```{r, cache = FALSE, message = FALSE, warning = FALSE}
library("riem")
library("dplyr")
france_airports <- riem_stations(network = "FR__ASOS")
marseilles_airport <- filter(france_airports, grepl("MARSEILLE", name) | grepl("Marseille", name))
marseilles_airport

```

# Get time series of temperature for Marseille airport

We'll transform it to daily average, and convert Fahrenheit to Celsius thanks to the `weathermetrics` package. We impute the missing values and remove outliers via the use of `forecast::tsclean`.


```{r, cache = FALSE, fig.width=8, fig.height=6, message = FALSE, warning = FALSE}
marseille <- riem_measures(station = marseilles_airport$id,
                           date_start = "2010 01 01")

marseille <- group_by(marseille, day = as.Date(valid))
marseille <- summarize(marseille, temperature = mean(tmpf))
marseille <- mutate(marseille, temperature = weathermetrics::fahrenheit.to.celsius(temperature))
library("ggplot2")


library("forecast")
marseille_ts = ts(as.vector(tsclean(marseille$temperature)), freq=365.25, start=c(2010, 1))
autoplot(marseille_ts) +
  ylab("Daily average temperature in Marseille airport (ºC)") +
  xlab("Time (days)")

```

# Forecast for Marseille

For this we use the `forecast` package. We use the `stlm` because our time series obviously present yearly seasonality.

```{r, cache = FALSE, fig.width=8, fig.height=6}

fit <- stlm(marseille_ts)
pred <- forecast(fit, h = 7)
# plot
theme_set(theme_gray(base_size = 14))
autoplot(pred) +
  ylab("Daily average temperature in Marseille airport (ºC)") +
  xlab("Time (days)") +
  ggtitle("How cold will I be during the holidays?",
          subtitle = "Data accessed via the rOpenSci riem package and forecasted with forecast")

```

Mmh I don't see anything, but `autoplot.forecast` has an `include` parameters, so I'll only plot the last 31 values.


```{r, cache = FALSE, fig.width=8, fig.height=6}

autoplot(pred, include = 31) +
  ylab("Daily average temperature in Marseille airport (ºC)") +
  xlab("Time (days)") +
  ggtitle("How cold will I be during the holidays?",
          subtitle = "Data accessed via the rOpenSci riem package and forecasted with forecast")
```

# What if I went somewhere else?

Ok, what if I had travelled to, say, Hyderabad in India?

```{r, echo = FALSE, cache = FALSE, fig.width=8, fig.height=6}

hyderabad <- riem_measures(station = "VOHY",
                           date_start = "2010 01 01")

hyderabad <- group_by(hyderabad, day = as.Date(valid))
hyderabad <- summarize(hyderabad, temperature = mean(tmpf))
hyderabad <- mutate(hyderabad, temperature = weathermetrics::fahrenheit.to.celsius(temperature))

hyderabad_ts = ts(as.vector(tsclean(hyderabad$temperature)), freq=365.25, start=c(2010, 1))
fit <- stlm(hyderabad_ts)
pred <- forecast(fit, h = 7)
autoplot(pred, include = 31) +
  ylab("Daily average temperature in Hyderabad airport (ºC)") +
  xlab("Time (days)") +
  ggtitle("Hyderabad forecasted temperatures in December 2016",
          subtitle = "Data accessed via the rOpenSci riem package and forecasted with forecast")

```

Without surprise, we forecast I'd have enjoyed warmer weather. 

I wouldn't advise you to really use such code to forecast temperature, but I'd recommend you to use `riem` for getting weather airport data quite easily and to dig more deeply into `forecast` functionalities if you're interested in time series forecasting. And stay warm!
